---
title: Assignment 01
author: TracyJi
date: '2021-05-21'
slug: assignment-01
categories:
  - ggplot2
tags: []
---
## Data Visualization Exercise 2

## 1. Temperature vs Pressure
We will study the relationship between temperature and pressure through a density plot

```{r echo = FALSE, warning = FALSE}
library(ggplot2)
ggplot(data = datasets::pressure, aes(x = pressure, fill = temperature)) +
  geom_density(adjust = 1, alpha = 0.5) +
  labs(
    title = "Pressure vs Temperature", 
    x = "Pressure (mercury in millimeters)", y = "Temperature (Celsius)",
    fill = "Temperature"
    )
```

* From the chart above we could easily found the temperature and pressure may have certain positive relation.

* However, we still need a larger sample to test our observations.

We could also use another plot to do this data visualization:

```{r message = FALSE, warning=FALSE}
library(ggplot2)
ggplot(data = datasets::pressure, aes(x = pressure)) +
  geom_boxplot() +
  labs(title = "Pressure vs Temperature",
       x = "Pressure(mercury in millimeters)",
       y = "Temperature(Celsius)") +
  theme(axis.ticks.y = element_blank(),
        axis.text.y = element_blank())
```



## 2. Performances Among Different Insect Sprays 

We will study the counts of insects in agricultural experimental units treated with different insecticides through a ridge plot

```{r message = FALSE, warning = FALSE}
library(ggridges)
ggplot(data = datasets::InsectSprays, aes(x = count, y = spray, fill = spray, color = spray)) + 
  geom_density_ridges(alpha = 0.5) +
  labs(title = "Counts of Insects of Different Insecticides", 
       x = "Count(units)",
       y = "Sprays",
       fill = "Sprays")
```

* From the ridge plot we could find Spray F performs better than others.

* Performances between Spray A and Spray B are quite similar.


We could use another simple plot to show the above data:

```{r echo=FALSE, warning=FALSE}
ggplot(datasets::InsectSprays, aes(x = count, y = spray, color = spray)) +
  geom_point(size = 2, alpha = 0.5) +
  labs(
    title = "How are the differences among Sprays?", 
    x = "Count (units)", y = "Sprays"
    ) +
  facet_grid(~ spray)

```

Discussion:
By doing this assignment, I have practiced several plots to do data visualization and it's quite interesting process for me to explore different plot types. However, I still think it is a bit harder for me to distinguish categorical and numerical data. So, I have tried so many data in datasets to find appropriate way to visualize them. The most difficult one I don't know how to deal with is "HairColorEye" data, and hope to know how could we visualize such kind of data. Thanks!