---
title: Assignment 2
author: Xiao Ji
date: '2022-06-18'
slug: assignment-2
categories: [logistic regression]
tags: []
---
Assignment 2 Bank Marketing Dataset

We Need:
a.Build a logistic regression model
b.We need to identify whether a customer will subscribe to a term deposit or not.
c.We need not use all the variables, If we are comfortable you can perform factor analysis on predictor variables.
d.Build a simple model and focus on interpretation and communication of our insights from the analysis.

```{r warning=FALSE, error=FALSE}
library(readr)
library(dplyr)
library(shiny)
library(readxl)
library(corrplot)
library(ggplot2)
library(janitor)
library(tidyverse)
library(caret)
library(AppliedPredictiveModeling)
library(e1071)
```
# Firstly,  we need load the Dataset(Bank Market Dataset) and clean it. 
```{r}
bankfull <- read_csv("bank-additional-full.csv")
## summarize a quick snapshot of our data set
summary(bankfull)
str(bankfull)
## Check for missing values
sum(is.na(bankfull))
```

*Here we found that there was no missing values in our dataset.