---
title: assignment 05
author: Xiao Ji
date: '2021-06-23'
slug: assignment-05
categories: []
tags: []
---

```{r}
library(GGally)
library(tidymodels)
```

Dataset: Diamonds
Desciption
* This dataset contains pricesc and other 9 attributes of more than 53,000 dimmonds. The variables are as follows:
```{r}
data("diamonds")
str("diamonds")
glimpse(diamonds)
```

Discoveries & Insights

First, we want to know the average/standard deviation/median pvalue of these diamonds
```{r}
diamonds %>% 
  mutate(m = mean(price),     # calculates the mean price
         sd = sd(price),      # calculates standard deviation
         med = median(price)) # calculates the median price

diamonds %>% 
  summarize(avg.price = mean(price),     # average price of all diamonds
            dbl.price = mean(price) * 2, # calculating double the average price
            random.add = 1 + 2,          # a math operation without an existing variable 
            avg.carat = mean(carat),     # average carat size of all diamonds
            stdev.price = sd(price)) 
```
Secondly, we want to know the distribution for all diamonds.
```{r}
diamonds %>% 
  ggplot(aes(x = price, group = cut, fill = cut)) +
  geom_histogram(binwidth = 10)
```
Thirdly, we might want to see how the quality of the cut, or the color, or the clarity, affects the price.
```{r}
ggplot(diamonds, aes(x=carat, y=price, color=clarity)) + geom_point()
```

Then, we could also improve the data representation by altering the transparency of the data points. What this does is showing us where the majority of the data points sit:The more data points that sit in a particular location (the darker the area), the more observations there are.

* Note:lower alpha values increase transparency of points
```{r}
diamonds %>% 
  ggplot(aes(x = depth, y = price)) +
  geom_point(alpha = 0.1) 

```

* Conclusion:from the plot above, we could find most diamonds have the depth ranging from 55-65mm.


## Create two histograms of the price variable and place them side by side on one output image.

* Note:The first plot is a histogram of price and the second plot has transformed the price variable using log10.

```{r}
library(gridExtra)

p1 <- ggplot(diamonds,(aes(x = price)))+
  geom_histogram(binwidth = 100, fill = I('#099DD9'))+
  ggtitle('Diamond prices')

p2 = ggplot(diamonds,(aes(x = log10(price))))+
  geom_histogram(binwidth = 0.05, fill = I('#F79420'))+
  ggtitle('log Price')

grid.arrange(p1,p2,ncol = 2)
```
## Create Correlation Matrix among variables.
```{r}
diamonds %>%
    mutate_if(is.factor,as.numeric) %>%
   select(price,everything()) %>%
    ggcorr(method = c("everything", "pearson"),label = T)
```



* Conclusion:From the matrix above, we find there are some highly-related variables. 

Thus, we could predict that there may be non-linear relationship between carat with price from the chart below.
```{r}
diamonds %>%
ggplot(aes(x=carat,y=price))+
  scale_y_continuous(trans=log_trans(),labels=function(x) round(x,-2))+
  geom_point()+
  geom_smooth(method="lm",formula="y~poly(x,4)")+
  theme_bw()
```

However, if we would rather show a best fit straight line rather than a curve, we can change the option in the geom_smooth layer.
```{r}
ggplot(diamonds, aes(x=carat, y=price)) + geom_point() + geom_smooth(se=FALSE, method="lm")
```
* Note: Above is the best fit line to the relationship between carat and price.

