---
title: Assignment 03
author: Tracy Ji
date: '2021-06-05'
slug: assignment-03
categories:
  - tidyverse
tags: []
---

## Import lego_sales.csv and find the most three common first names in customers are :Jackson	13, Jacob	11 and Joseph	11	
```{r}
library(tidyverse)
read_csv("lego_sales.csv")
lego_sales %>%
  mutate(first_name = fct_infreq(first_name)) %>%
  count(first_name)

```

## Find the most three common themes are Star Wars	75, Nexo Knights	64, and Gear/Mixels	55
```{r}
library(tidyverse)
read_csv("lego_sales.csv")
lego_sales %>%
  mutate(theme = fct_infreq(theme)) %>%
  count(theme)
 
```

## Find the most three common subthemes under above situation are "The Force Awakens", "Series 9", "Role-Play toys	7 & Stationery	7"
```{r}
library(tidyverse)
read_csv("lego_sales.csv")
lego_sales %>%
  filter(theme == "Star Wars") %>%
  count(subtheme, sort = TRUE)

```

```{r}
library(tidyverse)
read_csv("lego_sales.csv")
lego_sales %>%
  filter(theme == "Gear") %>%
  count(subtheme, sort = TRUE)
```

```{r}
library(tidyverse)
read_csv("lego_sales.csv")
lego_sales %>%
  filter(theme == "Mixels") %>%
  count(subtheme, sort = TRUE)
```

## Create a new variable called age_group and group the ages into the following categories: “18 and under”, “19 - 25”, “26 - 35”, “36 - 50”, “51 and over”.
```{r}
lego_sales <- lego_sales %>%
  mutate(age_group = case_when(age <= 18 ~ "18 and under", age >= 19 & age <= 25 ~ "19 - 25", age >= 26 & age <= 35 ~ "26 - 35", age >= 36 & age <= 50 ~ "36 - 50", age >= 51 ~ "51 and over" ))
```

## The probability of a randomly selected customer in the 19-25 age group is 20.8% 
```{r}
lego_sales %>%
  count(age_group, sort = TRUE) 
```

## The probability a randomly selected customer is in the 19-26 age group and purchased a Duplo theme set is 9/129
```{r}
lego_sales %>%
  filter(age_group == "19 - 25") %>%
  count(theme == "Duplo", sort = TRUE) 
```

## The probability a randomly selected customer is in the 19-26 age group given purchased a Duplo theme set is 9/35
```{r}
lego_sales %>%
  filter(theme == "Duplo") %>%
  count(age_group == "19 - 25", sort = TRUE)
```

## Which age group has purchased the largest number of lego sets? How many did they purchase?
```{r}
lego_sales %>% 
  group_by(age_group) %>% 
  summarise(total_number = sum(quantity) ) %>%
  arrange(desc(total_number))
```

* It can be seen that 36-50 age group has purchased the most lego sets (313)

## Which age group has spent the most money on legos? How much did they spend?
```{r}
lego_sales %>%
  mutate(money_spent = us_price * quantity
  ) %>%
  group_by(age_group) %>%
  summarise(total_spent = sum(money_spent)
  ) %>%
  arrange(desc(total_spent))
```

* The outcome is that age group of 36-50 has spent the most on lego sets with amount $9532.87.

## My question would be: "Which theme has made up the most revenue in 2018?"
```{r warning = FALSE}
lego_sales %>%
  mutate(money_spent = us_price * quantity
  ) %>%
  group_by(theme) %>%
  summarise(total_spent = sum(money_spent)
  ) %>%
  arrange(desc(total_spent)) 
 
```
* Of course, the answer is "Star Wars".

## Visualization of the above result
```{r}
library(tidyverse)
lego_sales %>%
  mutate(money_spent = us_price * quantity
  ) %>%
  group_by(theme)%>%
 summarize(total_spent = sum(money_spent)) %>%
  ggplot(aes(x = total_spent, y = theme, color = theme)) +
  geom_point() +
  coord_polar(theta = "x")
```
## Change above visualization
```{r}
library(tidyverse)
lego_sales %>%
  mutate(money_spent = us_price * quantity
  ) %>%
  group_by(theme)%>%
 summarize(total_spent = sum(money_spent)) %>%
  ggplot(aes(x = total_spent, y = theme, color = total_spent)) + 
  geom_point()
```

* I add this annotation to identify I have changed the color of the above result


